A Survey of Range-Only SLAM Techniques and Sensors

### 2018-02-05 Paper.tex
Spelling corrections

	A method proposed by \cite{Dios2015} is geared towards improving map building speed and accuracy for UAS dealing with the 3D RO-SLAM problem. The 3D RO-SLAM problem refers to the added complexity that devices such as submersibles \cite{Newman} and aerial vehicles experience when having to operate in an environment where three dimensions must be considered as opposed to the planar environment many robots are assumed to operate in. The method utilizes inter-beacon measurements and a novel mode selection which is used to select a measurement gathering method based on current conditions \cite{Dios2015}. The first mode is noted as mapping (MS) and the second localization (LS). When in mapping mode the measurment are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations. Based on experimentation performed by \cite{Dios2015} the method performed well and a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.

@@

	\cite{Fabresse2013} presents a solution for the 3D RO-SLAM problem. The solution reduces computational load through reduced spherical parametrization of map feature positions. The paper also proposes a new EKF update method which incorporates a reduced spherical representation of the state vector. In addition the paper describes how to efficiently integrate multi-modal belief of elevations angles and azimuth from a range sensor into the EKF utilizing two independent Gaussian Mixtures \cite{Fabresse2013}. In addition \cite{Fabresse2014} expands upon this by presenting a pre-filtering algorithm to be applied to range measurment before being used in the EKF in order to reduce the effect of noise generated by environmental issue such as multipathing. It is then proposed by \cite{Fabresse2015} that the above method can be utilized for decentralized multi-SLAM with range only sensors. This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving localization estimation. Based on experimental results obtained by \cite{Fabresse2015} the integration of estimates from multiple robots of the same landmarks provides a benefit to landmark localization over a single robot. In \cite{Fabresse2016} the author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).

@@

Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented. An IF algorithm is mentioned in\cite{Torres-Gonzalez2014}. In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the gausiians in their conical parameterization which is comprised of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
Sparse Extended information filters is derived from the information filter Information filters but it maintains a sparse representation of the information matrix. This makes the SEIF more scalable and efficient as show in\cite{Torres-Gonzalez2014}

The information filter stores the relation between any 2 state elements in the information matrix also known as links. The higer the vlaue of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robot s state . SEIF maintains a sparse information matrix by eliminating weak inks that are below a certain threshold thus reducing the computational complexity involved .

In \cite{Torres-Gonzalez2014} they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the preditcition stage of the iteration, send the information to the beacons where they compute the update of the process. Hence the computer burden on the robot is reduced. In addition they factored in inter beacon measurements to reduce uncertainity even furthur. In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM mehtod using EKF.

@@

It represents the information in the form of a graph as show in figure. The nodes in the graph represent the robots path and the landmarks. The edges between them represents the spatial  constraints between them also known as information constraints. These constraints ae then linearised and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in \cite{Grisetti}.

\subsection{Particle}      %change the references
Particles filters are made ue up various monte carlo algorithms. they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}. In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem\cite{Engelson1992} which EKF in comparison has it drawbacks. It has also been at the core higher dimensional computational problems.  
%Description
Initially robot assumes global uncertainity through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
\begin{figure}[h!]
	\centering
	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the robot location. }

\end{figure}
Assuming at time t=0;we have N particles equally space in the enviornment that are drawn based on a uniform distribution $ p(x_oa)$.                                                                        resampling methods depending on computational complexities. After some iterations only th   p
Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$. It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$. Eventually the particle filter converges to give us the true positioning of the robot.

@@

	\subsection{Fast SLAM}
	EKF is mainly used when we have a non-linear dynamic system model which has Gaussian noise.The quadratic complexity due to Gaussian approximations of higher dimensions make the covariance matrix very large. This eventually causes higher complexity and leads to the divergence of the filter. The single data association problem also adds to this complexity. FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem. This allows it handle system models with non gaussians noise as well. This results in the computational complexity to grow logarithmically instead of quadratic growth.

	FastSLAM utilizes the conditional Independence property of SLAM applications. If the path of the robot is known the correlation between the landmarks becomes zero. Hence in FastSLAM the robot path is initialised by using a particle fitler. Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{Yuan2012}. Thus it maintains mutliple data hypothesis overcoming the EKF problem.

	As mentioned in \cite{Thrun2002a} the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficency. In order to overcome this Rao blackwe the algorithm was tweaked to have a better target distrubtion in FASTSLAM 2.0. It was called the Rao-Blackwellized particle filter as mentioned in \cite{Montemerlo2003}

>>>>

	A method proposed by \cite{Dios2015} is geared towards improving map building speed and accuracy for UAS dealing with the 3D RO-SLAM problem. The 3D RO-SLAM problem refers to the added complexity that devices such as submersibles \cite{Newman} and aerial vehicles experience when having to operate in an environment where three dimensions must be considered as opposed to the planar environment many robots are assumed to operate in. The method utilizes inter-beacon measurements and a novel mode selection which is used to select a measurement gathering method based on current conditions \cite{Dios2015}. The first mode is noted as mapping (MS) and the second localization (LS). When in mapping mode the measurement are integrated with a high probability to quickly create a map, when in localization mode the probability is lowered to create higher accuracy localizations. Based on experimentation performed by \cite{Dios2015} the method performed well and a general increase in accuracy and map speed was noted, however it is stated that a wider variety of experimentation should be performed to validate the overall robustness and effectiveness of the method.

@@

	\cite{Fabresse2013} presents a solution for the 3D RO-SLAM problem. The solution reduces computational load through reduced spherical parametrization of map feature positions. The paper also proposes a new EKF update method which incorporates a reduced spherical representation of the state vector. In addition the paper describes how to efficiently integrate multi-modal belief of elevations angles and azimuth from a range sensor into the EKF utilizing two independent Gaussian Mixtures \cite{Fabresse2013}. In addition \cite{Fabresse2014} expands upon this by presenting a pre-filtering algorithm to be applied to range measurement before being used in the EKF in order to reduce the effect of noise generated by environmental issue such as multipath. It is then proposed by \cite{Fabresse2015} that the above method can be utilized for decentralized multi-SLAM with range only sensors. This new method would allow for landmarks estimated by a robot to be incorporated into the estimation of another nearby robot, thus improving localization estimation. Based on experimental results obtained by \cite{Fabresse2015} the integration of estimates from multiple robots of the same landmarks provides a benefit to landmark localization over a single robot. In \cite{Fabresse2016} the author also validates and expands upon this method through indoor and outdoor experimentation with an Unmanned Aircraft System (UAS).

@@

Information filters work on same underlying Gaussian belief principle as that of EKF but vary in the way the Gaussian beliefs are represented. An IF algorithm is mentioned in\cite{Torres-Gonzalez2014}. In EKF the gaussians are represented in the form of their moments; mean and variance, whereas in a information filter the Gaussians in their conical parameterization which comprises of a information matrix and information vector.Hence what is computational complex in EKF is simple in the other and vice versa. Hence they are dual to each other.
Sparse Extended information filters is derived from the  information filter but it maintains a sparse representation of the information matrix. This makes the SEIF more scalable and efficient as show in\cite{Torres-Gonzalez2014}

The information filter stores the relation between any 2 state elements in the information matrix also known as links. The higher the value of the link the stronger is the relationship between the 2 state variables and the more it is gonna effect the robots state. SEIF maintains a sparse information matrix by eliminating weak inks that are below a certain threshold thus reducing the computational complexity involved .

In \cite{Torres-Gonzalez2014} they further reduce the computational complexity of by utilizing the computational capabilities of the nodes or radio  beacons. Here the robot computes the prediction stage of the iteration, send the information to the beacons where they compute the update of the process. Hence the computer burden on the robot is reduced. In addition, they factored in inter beacon measurements to reduce uncertainty even further. In \cite{Torres-Gonzalez2017} it evaluates and compares  the SEIF method for 3d SLAM using an octorotor In conclusion this method had better estimates and lesser computational burden than the traditional RO SLAM method using EKF.

@@

It represents the information in the form of a graph as show in figure. The nodes in the graph represent the robots path and the landmarks. The edges between them represents the spatial  constraints between them also known as information constraints. These constraints ae then linearized and are applied through standard inference techniques to acquire the full posterior.A manifold graph SLAM algorithm has been mentioned in \cite{Grisetti}.

\subsection{Particle}      %change the references
Particles filters are made ue up various monte carlo algorithms. they are used to estimate states in partially observable Markov chains as shown in \cite{Doucet2001}. In  initial applications particle filters were used in the field of localization where it was used to estimate a robots pose from sensor data. It is considered better and more robust to conventional estimation methods because it was able to solve the global localization[2] and the kidnapped robot problem\cite{Engelson1992} which EKF in comparison has it drawbacks. It has also been at the core higher dimensional computational problems.  
%Description
Initially robot assumes global uncertainty through a set of particles that are distributed all over the map. Hence both the robot and the landmarks are uncertain.As the robot moves around and measures sensor data it resamples the particle set weighted according to the probability of the particle being the right one. There are several resampling methods depending on computational complexities \cite{Li2015} After some iterations only the particles which have a high degree of probability  remain and eventually converge to the state of the robot and the landmarks.
\begin{figure}[h!]
	\centering
	\includegraphics[height=40mm,width=90mm]{Particle_filter_method.JPG}
	\caption{The leftmost image describes the state of the robot when it just initializes the particle filter. The particles are uniformly distributed.The image in the center describes the particle filter after a couple of iterations. Only the particles which have a higher probability are re sampled. The image on the right shows the particle filter eventually converging to estimate the robot location. }

\end{figure}
Assuming at time t=0;we have N particles equally space in the environment that are drawn based on a uniform distribution $ p(x_oa)$.                                                                        re sampling methods depending on computational complexities. After some iterations only th   p
Once the robot starts moving it collects measurements and at time $t>0$ we sample a new particle set $x^{[i]}_t$ for each particle in $x^{[i]}_{(t-1)}$. It is sampled based on the probability of measurement $p(z_t|x^{[i]}_{(t-1)})$. Eventually the particle filter converges to give us the true positioning of the robot.

@@

	\subsection{Fast SLAM}
	EKF is mainly used when we have a non-linear dynamic system model which has Gaussian noise.The quadratic complexity due to Gaussian approximations of higher dimensions make the covariance matrix very large. This eventually causes higher complexity and leads to the divergence of the filter. The single data association problem also adds to this complexity. FastSLAM uses multiple hypothesis data association through particle filtering to overcome this problem. This allows it handle system models with non Gaussians noise as well. This results in the computational complexity to grow logarithmically instead of quadratic growth.

	FastSLAM utilizes the conditional Independence property of SLAM applications. If the path of the robot is known the correlation between the landmarks becomes zero. Hence, in FastSLAM the robot path is initialized by using a particle filter. Once the set of poses representing the path is obtained it estimates the landmark positions using EKF over the entire robot path as mentioned in \cite{Yuan2012}. Thus, it maintains multiple data hypothesis overcoming the EKF problem.

	As mentioned in \cite{Thrun2002a} the initial FAST SLAM algorithm  FASTSLAM 1.0  suffered from sample inefficiency. In order to overcome this the algorithm was tweaked to have a better target distribution in FASTSLAM 2.0. It was called the Rao-Blackwellized particle filter as mentioned in \cite{Montemerlo2003}
